---
title: "Lab 8 - Linear Regression in R"
author: "Sara Orofino"
date: "11/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#{.tabset}
```{r, message = FALSE, include=FALSE}
library(tidyverse)

salmon <- read_csv("salmon.csv")
```

## Part 1.

Linear Regression in R:

```{r}
salmon_model <- lm(salmon_fresh ~ year, data = salmon)
salmon_model

# slope of the model: y = 7550x - 14982940

```
Imports of fresh salmon (1000 pounds) = -14982940 + 7550(year)

Slope: The slope of the model indicates that for every increase year there is an increase in imports of fresh salmon of 7550 (1000 pounds). 

Y-intercept: At year 0, there was a negative import of fresh salmon equal to 1,498,240 (1000 pounds). This is concerning because there shouldn't be a negative value of imports. The lowest the imports should be is zero. Likely this indicates that the model can't be used to accurately assess past values for fresh salmon imports (1000 pounds). 

## Part 2. 

```{r, echo = FALSE}
par(mfrow = c(2,2))
  plot(salmon_model) # use this code to get all four plots side-by-side in knitted document 
```

  
Normality: Residuals appear to be mostly normally distributed, however there are a handful of lower outliers that might be slightly skewing the data. 

Heteroscedasticity: most of the values appear to fall above the line, where they should be falling in a random pattern mostly evenly about the dotted line.

Outliers: there are a handful of lower outliers that are concering, but if the measurement collection was sound, they should not be excluded. 

##Part 3.

1. Does the year significanly predict salmon imports?  
  
Yes, the model significantly predicts salmon imports p-value < 0.001.  
  
2. What does the R^2^ value actually mean in words?  
  
R^2^ = 0.9478  94.78% of the variance in fresh salmon imports is explained by this model (year).   
  
3. What proportion of the variance of salmon imports is NOT explained by year?  
  
6.22% of the variance of fresh salmon imports is NOT explained by this model (year).  

##Part 4. 

Create a finalized graph of fresh salmon imports by year. 

```{r}
salmon_final_graph <- ggplot(salmon, aes(x = year, y = salmon_fresh)) + geom_point() +
geom_smooth(method = lm, se = TRUE, size = 0.5, color = "gray20") + theme_bw() +
scale_x_continuous(expand = c(0,0), limits = c(1990, 2017)) +
labs(x = "Year", y = "U.S. Annual Fresh Salmon Imports\n(1,000 pounds)")
salmon_final_graph
```

##Part 5.

Making predictions using the model:

1. Make a data frame called new_years containing the sequence of years that we want to make predictions for. *Note: column name we create is the **SAME** as the variable name 'year' that the model uses*  
   
2. Feed that data frame into the predict() function, letting it know which model to use to make prediction for the new values.

Include interval = "confidence" to also report the lower and upper bounds of the 95% CI for model fit at each year.  
  
3. Bind the predicted outcomes (those are the values in the column 'fit') with the 'new_year' data to actually careate a useful table of predicted imports and upper and lower CI.    

```{r}
new_years <- data.frame(year = c(2022, 2024, 2026, 2028)) #1

future_predict <- predict(salmon_model, newdata = new_years, interval = "confidence") #2
future_predict

predictions <- data.frame(new_years, future_predict) #3
predictions

```

##Part 5. 

Find Pearson's R (correlation)  

1. Use the cor() function to find pearson's r for the linear relationship described between the year and fresh salmon imports.    


```{r}
salmon_cor <- cor(salmon$year, salmon$salmon_fresh)

# output 0.9735387
```
  
2. Would you describe this as a weak/strong negative/positive correlation?  
  
There is a strong positive relationship between year and fresh salmon imports (pearson's r = 0.9735).  








